---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xlr or 'Exceller'

<!-- badges: start -->
[![R-CMD-check](https://github.com/NHilder/xlr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/NHilder/xlr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# xlr 
xlr is designed to help build summary tables with complex survey data, and export data to `Excel`. It
includes functions to easily make cross-tabulations, work with multiple response data, and question
blocks. It supports labelled data that can be generated from the popular survey platform Qualtrics.

It makes exporting data from `Excel` easier. It is a easier to use wrapper around [openxlsx](https://ycphs.github.io/openxlsx/).
It supports tables with footnotes, headers, and generating table of contents in `Excel` documents. It 
is not fully featured, but designed to be used when you are moving either statistical summaries
or tables from R into `Excel`.

This package is designed to work seamlessly with [tidyverse](https://www.tidyverse.org/) family 
of functions.

It is currently experimental and subject to change based on peoples feedback.

## Installation
``` r
# To install via CRAN
install.packages("xlr")
```

You can install the development version of xlr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("NHilder/xlr")
```

## Example

This is a example of how to create a two-way table, fix the formatting for that table, and then
export that table to `Excel`.

```{r example}
library(xlr)
library(dplyr)

# create a summary table
two_way_table <- build_table(mtcars,c(cyl,gear))
two_way_table

# make the percentage have two decimal places using dplyr
two_way_table <- two_way_table |> 
  mutate(Percent = xlr_percent(Percent, dp = 2))

# write the data to an xlsx file
write_xlsx(two_way_table,
           "example.xlsx",
           "an example")
```

Check out the vignettes for more information on how to use the package.
